### 2020-05-29 README.Rmd
update 2020-05-29 11:52:21

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
[![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969)
[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://CRAN.R-project.org/package=worcs)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

>>>>

<!-- README.md is generated from README.Rmd. Please edit that file -->
[![CRAN status](https://www.r-pkg.org/badges/version/worcs)](https://cran.r-project.org/package=worcs)
[![metacran downloads](https://cranlogs.r-pkg.org/badges/worcs)](https://cran.r-project.org/package=worcs)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![Travis build status](https://travis-ci.org/cjvanlissa/worcs.svg?branch=master)](https://travis-ci.org/cjvanlissa/worcs)
[![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969)
<!--[![Codecov test
coverage](https://codecov.io/gh/cjvanlissa/worcs/branch/master/graph/badge.svg)](https://codecov.io/gh/cjvanlissa/worcs?branch=master)-->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->
